Imperfect slope measurements drive overestimation in geometric cone model of lake and reservoir depth

### 2021-12-06 manuscript/manuscript.Rmd
typo fix
add doi link

# Optional: line of arbitrary text with additional information.
# Could be used, for example, to mention the bibliographic info in a post-print.
# If not specified, defaults to "This version was compiled on \today"
date_subtitle: > 
  This is an Accepted Manuscript of an article to be published by Taylor & Francis in Inland Waters.

>>>>

# Optional: line of arbitrary text with additional information.
# Could be used, for example, to mention the bibliographic info in a post-print.
# If not specified, defaults to "This version was compiled on \today"
date_subtitle: > 
  This is an Accepted Manuscript of an article published by Taylor & Francis in Inland Waters, available online: \href{https://doi.org/10.1080/20442041.2021.2006553}{doi:10.1080/20442041.2021.2006553}
